<header style="text-align: center">

### 2019-05-22 report/report.Rmd
Add UFO flights tables and update TODO lists

## Air Traffic Evolution

@@

@@

```{r, fig.align='center'}
datatable(info[, .(orig, dest, airline, diff, fuel)], options = list(dom = 'tp', columnDefs = list(list(className = 'dt-center', targets = '_all'))), colnames = c('Origin', 'Destination', 'Airline', 'Distance Delta (NM)', 'Fuel Delta (kg)')) %>%
	formatRound(columns = c('diff', 'fuel'), digits = 2)
```

On average, airlines actually saved `r format(abs(info[, mean(fuel)]), digits = 3)` kg of fuel by diverting flights to airports closer to the origin point.

@@

```{r, fig.align='center'}
ddr.jsmap(data$real$routes[id %in% div[, id]], info, coord)
```

@@

## TODO

- N flights vs. time with orig/dest at EBBR
- N diverted flights vs. time with dest EBBR

@@

Find # of flights in nearby airports

@@

- Statistics (mean + sigma) for delays on each airport per day

@@

>>>>

## Air Traffic Evolution {.tabset .tabset-fade}

@@

- Find average before/after (get % difference)

Bizarrely, despite the airport supposedly being closed from March 22 to April 3, the number of flights during the days following the attack is non-zero. Let's take a closer look at these flights:

### EBBR Departures {-}

```{r}
datatable(ufo[orig == bru, .(dest, airline, aircraft, takeoff, landing)], options = list(dom = 'tp', columnDefs = list(list(className = 'dt-center', targets = '_all'))), colnames = c('Destination', 'Airline', 'Aircraft', 'Departure', 'Arrival')) %>%
	formatDate(columns = c('takeoff', 'landing'), method = 'toLocaleString')
```

### EBBR Arrivals {-}

```{r}
datatable(ufo[dest == bru, .(orig, airline, aircraft, takeoff, landing)], options = list(dom = 'tp', columnDefs = list(list(className = 'dt-center', targets = '_all'))), colnames = c('Origin', 'Airline', 'Aircraft', 'Departure', 'Arrival')) %>%
	formatDate(columns = c('takeoff', 'landing'), method = 'toLocaleString')
```

@@

```{r, fig.align='center'}
datatable(div[, .(orig, dest, airline, diff, fuel)], options = list(dom = 'tp', columnDefs = list(list(className = 'dt-center', targets = '_all'))), colnames = c('Origin', 'Destination', 'Airline', 'Distance Delta (NM)', 'Fuel Delta (kg)')) %>%
	formatRound(columns = c('diff', 'fuel'), digits = 2)
```

On average, airlines actually saved `r format(abs(div[, mean(fuel)]), digits = 3)` kg of fuel by diverting flights to airports closer to the origin point.

@@

```{r, fig.align='center'}
ddr.jsmap(data$real$routes[id %in% div[, id]], div, coord)
```

@@

@@

- Find # of flights in nearby airports vs. time (group time series)

@@

- Delays on each airport vs. time (per hour)
- Boxplot (mean + sigma) comparing average delays on each airport (while EBBR closed)
- Find average delay before/during/after

@@

- Find from total flights the airlines that were most affected (from those that travel to EBBR)
- Average delays (while EBBR closed) by airline
